04_analysis

### 2024-01-24 05_analysis.Rmd
Update 05_analysis.Rmd
removed loud event part, moved to different rmd

for (ft in ftlist) {
  df <- readRDS(ft)
  assign(paste0("GPSwhaleAISenvSS", substr(ft, 29, 30)), df)
}
```

@@

# Create a new column that specifies the drift number before the bind.
for (col in dlist){
  data <- get(col) %>% mutate(Deployment = substr(col,17,18))
  data <- data[data$species %in% c(NA, "ZC", "PM", "BB", "BW43"),]    # Remove BW37V and BWC from analysis as there are too few detections.
  assign(paste0("GPSwhaleAISenvSS", substr(col,17,18)), data)
}

# Bind and save allDrifts dataframe
allDrifts <- rbind(GPSwhaleAISenvSS07, GPSwhaleAISenvSS08, GPSwhaleAISenvSS10, GPSwhaleAISenvSS12,
                   GPSwhaleAISenvSS13, GPSwhaleAISenvSS14, GPSwhaleAISenvSS16, GPSwhaleAISenvSS18,
                   GPSwhaleAISenvSS19, GPSwhaleAISenvSS20, GPSwhaleAISenvSS21, GPSwhaleAISenvSS22,
                   GPSwhaleAISenvSS23)

# Remove points where buoy is on the shelf - 300 meters
allDrifts <- allDrifts %>%
  filter(depth > 300)

@@

Compare overall TOL2000sound levels when whales are absent vs. present
```{r}
ggplot(allDrifts, aes(factor(Wpresence), TOL_2000)) + geom_boxplot()
```

Scatterplots

```{r}
# SST vs TOL 2000
ggplot(data = allDrifts, aes(x = sst_mean, y = `TOL_2000`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# SST over time (strange plot)
ggplot(allDrifts, aes(x = UTC, y = sst_mean)) +
  #geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")

# Depth vs TOL 125
ggplot(data = allDrifts, aes(x = `TOL_125`, y = depth *(-1))) +
  #geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)

# Chlorophyll vs TOL 125
ggplot(data = allDrifts, aes(x = chlorophyll_mean, y = `TOL_125`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# CHl over time
ggplot(allDrifts, aes(x = UTC, y = chlorophyll_mean)) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)
  #geom_smooth(method = "loess")

# Mixed Layer Depth vs TOL125 with species
ggplot(data = allDrifts, aes(x = mldDepth, y = `TOL_125`)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

# Mixed Layer Depth over time
ggplot(allDrifts, aes(x = UTC, y = mldDepth*(-1))) +
  geom_line() +
  geom_point(aes(color = species)) +
  scale_color_discrete(na.translate=FALSE)

ggplot(data = allDrifts, aes(x = `TOL_125`, y = bathy_slope)) +
  geom_point(aes(color = species)) + scale_color_discrete(na.translate=FALSE)

>>>>

for (ft in ftlist) {
  df <- readRDS(ft)
  assign(paste0("GPSwhaleAISenvSS", substr(ft, 29, 30)), df)
}

GPSwhaleAISSS20.alt <- readRDS("D:Buoy_dfs/GPSwhaleAISSS20_alt.rda")
```

@@

# Create a new column that specifies the drift number before the bind.
for (col in dlist){
  data <- get(col) %>% mutate(Deployment = as.numeric(substr(col,17,18)))
  data <- data[data$species %in% c(NA, "ZC", "PM"),]    # Remove all but ZC and PM from analysis as there are too few detections.
  assign(paste0("GPSwhaleAISenvSS", substr(col,17,18)), data)
}

# Remove points where buoy is on the shelf - 300 meters
#Only occurs with buoy 7
GPSwhaleAISenvSS07 <- GPSwhaleAISenvSS07 %>%
  filter(depth > 300)
saveRDS(GPSwhaleAISenvSS07, file = "data/GPSwhaleAISenvSS07.rda")
saveRDS(GPSwhaleAISenvSS07, 'D:/Buoy_dfs/GPSwhaleAISenv07.rda')

# Bind and save allDrifts dataframe
allDrifts <- rbind(GPSwhaleAISenvSS07, GPSwhaleAISenvSS08, GPSwhaleAISenvSS10, GPSwhaleAISenvSS12,
                   GPSwhaleAISenvSS13, GPSwhaleAISenvSS14, GPSwhaleAISenvSS16, GPSwhaleAISenvSS18,
                   GPSwhaleAISenvSS19, GPSwhaleAISSS20.alt, GPSwhaleAISenvSS21, GPSwhaleAISenvSS22,
                   GPSwhaleAISenvSS23)

@@

Compare overall TOL2000sound levels when ALL whales are absent vs. present
```{r}
ggplot(allDrifts, aes(factor(Wpresence), TOL_2000)) + geom_boxplot()
```
